\tool: Revisiting BadUSB with Type-C

### 2021-03-20 WOOT/Files/badusb.tex

First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.

>>>>

First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices. This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next. Existence of such a feedback channel largely strengthens the attack ability of \tool.
